Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2020-10-12 papers/paper/paper.tex
Added ob time plot on paper
Added small edits to plotting script
Fixed fac because of renaming

\section*{Plots from MC}
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:step_length_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
\label{fig:step_length_prob_den}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}

>>>>

\section*{Plots from MC}
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:step_length_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
\label{fig:step_length_prob_den}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563.pdf}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_5.50e+09_1.00e+09_0.08_1.05_0.36.pdf}
\caption{\textbf{Onebounnd Time} Dimentions: $s$.}
\label{fig:ob_time}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563.pdf}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}
